---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(424342)
```

# lorem::ipsum()

<!-- badges: start -->
<!-- badges: end -->

* Quickly generate lorem ipsum placeholder text with `lorem::ipsum()`.

* Easy to integrate in RMarkdown documents. 

* Includes an RStudio addin to insert *lorem ipsum* into the current document.

## Installation

``` r
# install.package("devtools")
devtools::install_github("gadenbuie/lorem")
```

## Usage

### RStudio Addin

**lorem** includes a simple addin for RStudio that 
adds placeholder _lorem ipsum_ text to the current source document.
The addin allows you to specify the number of desired paragraphs and sentences.

### R Markdown

The easiest way to generate _lorem ipsum_ placeholder text is to call 
`lorem::ipsum()` in an inline R chunk in R Markdown.

```markdown
`r knitr::inline_expr("lorem::ipsum(paragraphs = 2)")`
```

`r paste(">", lorem::ipsum(2), collapse = "\n>\n")`

You can control the number of `paragraphs` and `sentences` per paragraph.

```markdown
`r knitr::inline_expr("lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))")`
```

`r paste(">", lorem::ipsum(3, 1:3), collapse = "\n>\n")`

You can also adjust the `avg_words_per_sentence` to create long or short paragraphs.

```markdown
`r knitr::inline_expr("lorem::ipsum(2, avg_words_per_sentence = 3)")`
```

`r paste(">", lorem::ipsum(paragraphs = 2, avg_words_per_sentence = 3), collapse = "\n>\n")`


```markdown
`r knitr::inline_expr("lorem::ipsum(1, avg_words_per_sentence = 20)")`
```

`r paste(">", lorem::ipsum(1, 2, avg_words_per_sentence = 20), collapse = "\n>\n")`

### Everywhere Else

Generate _lorem ipsum_ anywhere else using `lorem::ipsum()` or `lorem::ipsum_words()`.

```{r results='asis'}
ipsum_items <- replicate(5, lorem::ipsum_words(5))
cat(paste("-", ipsum_items), sep = "\n")
```

## Ipsum gratiam

Thank you to 
[Luke Haas](https://getlorem.com) 
for the node module 
[getlorem](https://github.com/lukehaas/getlorem) 
and for providing the lorem ipsum word list used in this package.
